Automatically generated NE tagged corpora for English and Hungarian

### 2012-07-03 paper/engNERwiki.tex
The examples for Common Noun pages in chapter 3 have been italicized.

Strictly speaking, our original assumption of equating WP articles with NEs is not valid: many pages describe common nouns (Book, Aircraft), calendar-related concepts (March 15, 2007), or other concepts that fall outside the scope of NER. To increase sentence coverage, we modified the algorithm to prevent it from misclassifying links to these pages as unknown entities and discarding the sentence.

>>>>

Strictly speaking, our original assumption of equating WP articles with NEs is not valid: many pages describe common nouns (\textit{Book}, \textit{Aircraft}), calendar-related concepts (\textit{March 15}, \textit{2007}), or other concepts that fall outside the scope of NER. To increase sentence coverage, we modified the algorithm to prevent it from misclassifying links to these pages as unknown entities and discarding the sentence.
